---
title: "Investigating Personality Traits with Respect to Academic Performance"
author: "By Anosh.S, Stuart.T, Matteus.R and Kshitij.M"
date: "April 19, 2019"
output: ioslides_presentation
widescreen: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)

# LOAD DATA v1 - uncomment the link below to: load data direct from html
setwd("C:/Users/anosh/Documents/Anosh's Data/!_Uni_!/Sem 1/DATA1001 - Intro to Data/Assignment 2")

resc = read.csv("Data/Responses.csv")

```

## Executive Summary

- Our study attempted to determine a correlation between personality traits and academic achievement 
- Data was acquired through a self-assessed survey, where participants answered questions pertaining to specific personal attributes and ATAR results were recorded
- Questions were then categorised by their respective personality trait - creativity, perseverance, and social intelligence

## IDA

- In 2014, the Australian government spent $13.8 billion on schools (APH, 2017)
- Education is a key concern in fostering sustainable economic development
- improvement of academic achievement amongst students is a fundamental premise in educational policies and management
- Subjective nature of the study with varying degrees of response, observer and selection bias
- Ethics regarding how candidates were informed 


## Investigating the Relationship Between Creativity and Academic Performance

- Balgiu and Adir (2013): no correlation between academic performance and creativity
- Academic Performance: Grades of students at the University Politehnica Bucharest
- Creativity: Performance in creative tasks (designing logos, etc.)

- Our Investigation: Promising results, but no solid conclusions which can be made
- Academic Performance: ATAR scores
- Creativity: Self evaluated response to psychometric questions

##
```{r, message = FALSE}
library(plotly)

Creativity.measure.1 <- resc$My.friends.say.that.I.have.lots.of.new.and.different.ideas.
Creativity.measure.2 <- resc$I.like.to.think.of.new.ways.to.do.things.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.


orcrea1 = factor(Creativity.measure.1, levels=levels(Creativity.measure.1)[c(4,2,1,3)])
orcrea2 = factor(Creativity.measure.2, levels=levels(Creativity.measure.2)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~orcrea1, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'My friends say that I have lots of new and different ideas'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.13,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 1a<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
    
      layout(
    title = "Actual ATAR Across Different Creative Types"
    , xaxis = x, yaxis = y) 
p1

```

##
```{r, message = FALSE}
library(plotly)
Creativity.measure.1 <- resc$My.friends.say.that.I.have.lots.of.new.and.different.ideas.
Creativity.measure.2 <- resc$I.like.to.think.of.new.ways.to.do.things.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.


orcrea2 = factor(Creativity.measure.2, levels=levels(Creativity.measure.2)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~orcrea2, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'I like to think of new ways to do things'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
   add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.13,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 1b<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Creative Types"
    , xaxis = x, yaxis = y) 
p1

```

##
```{r, message = FALSE}
library(plotly)
Creativity.measure.1 <- resc$My.friends.say.that.I.have.lots.of.new.and.different.ideas.
Creativity.measure.2 <- resc$I.like.to.think.of.new.ways.to.do.things.
Creativity.measure.3 <- resc$Being.able.to.come.up.with.new.and.different.ideas.is.one.of.my.strong.points.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.


orcrea3 = factor(Creativity.measure.3, levels=levels(Creativity.measure.3)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~orcrea3, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'Being able to come up with new and different ideas is one of my strong points'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
   add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.13,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 1c<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Creative Types"
    , xaxis = x, yaxis = y) 
p1

```

## Investigating the Relationship Between Perseverance and Academic Performance

- Perseverance is persistence of doing something despite difficulty or delay in achieving success
- Associated with growth mindsets
- No conclusive evidence highlighting a clear correlation
- However, through Robbins, Oh, Le, & Button, 2009, a clear relationship is confounded by other situational variables outside of the students' control such as socioeconomic status

## 
- Box-plots posing inconsistencies in the median with large spreads across all qualitative measures of relating to perseverance with respect to actual ATAR performance (figures 2a, 2b, 2c)

```{r, message = FALSE}
library(plotly)
Perseverance.measure.1 <- resc$I.believe.it.is.best.to.forgive.and.forget.
Perseverance.measure.2 <- resc$I.finish.things.despite.obstacles.in.the.way.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

orper1 = factor(Perseverance.measure.1, levels=levels(Perseverance.measure.1)[c(4,2,1,3)])
orper2 = factor(Perseverance.measure.2, levels=levels(Perseverance.measure.2)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~orper1, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'I believe it is best to forgive and forget'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
   add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.18,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 2a<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Perseverance Types"
    , xaxis = x, yaxis = y) 
p1

```

##
```{r, message = FALSE}
library(plotly)
Perseverance.measure.1 <- resc$I.believe.it.is.best.to.forgive.and.forget.
Perseverance.measure.2 <- resc$I.finish.things.despite.obstacles.in.the.way.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

orper1 = factor(Perseverance.measure.1, levels=levels(Perseverance.measure.1)[c(4,2,1,3)])
orper2 = factor(Perseverance.measure.2, levels=levels(Perseverance.measure.2)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~orper2, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'I finish things despite obstacles in the way'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
   add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.18,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 2b<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Perseverance Types"
    , xaxis = x, yaxis = y) 
p1

```

##
```{r, message = FALSE}
library(plotly)
Perseverance.measure.1 <- resc$I.believe.it.is.best.to.forgive.and.forget.
Perseverance.measure.2 <- resc$I.finish.things.despite.obstacles.in.the.way.
Perseverance.measure.3 <- resc$I.know.that.I.will.succeed.with.the.goals.I.set.for.myself.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

orper1 = factor(Perseverance.measure.1, levels=levels(Perseverance.measure.1)[c(4,2,1,3)])
orper2 = factor(Perseverance.measure.2, levels=levels(Perseverance.measure.2)[c(4,2,1,3)])
orper3 = factor(Perseverance.measure.3, levels=levels(Perseverance.measure.3)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~orper3, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'I know that I will succeed with the goals I set for myself'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
   add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.18,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 2c<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Perseverance Types"
    , xaxis = x, yaxis = y) 
p1

```

##
- Furthermore, weak correlation is ascertained via regression analysis
- Hence need to consider confounders e.g. socioeconomic factors

```{r, message = FALSE}
Perseverance.measure.1 <- resc$I.believe.it.is.best.to.forgive.and.forget.
Perseverance.measure.2 <- resc$I.finish.things.despite.obstacles.in.the.way.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

orper1 = factor(Perseverance.measure.1, levels=levels(Perseverance.measure.1)[c(4,2,1,3)])
orper2 = factor(Perseverance.measure.2, levels=levels(Perseverance.measure.2)[c(4,2,1,3)])

fit <- lm(aATAR ~ eATAR, data = resc)

x <- list(
  title = "Expected ATAR"
)

y <- list(
  title = "Actual ATAR"
)

p1 <- plot_ly(resc, x = ~eATAR, y = ~aATAR, color = ~orper1, type = "scatter", mode = "markers", 
        marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1"), text = ~paste("I believe it is best to forgive and forget: ", Perseverance.measure.1, '<br>Expected ATAR:', eATAR,'<br>Actual ATAR:', aATAR)) %>%
  
  add_lines(
    x = ~eATAR,
    y = fitted(fit),
    showlegend = FALSE
  )%>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.57,
    y = 1.02,
    size = 2,
    text = "<b><i>'I believe it is best to forgive and forget'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  
   add_annotations(
    xref = "paper",
    yref = "paper",
    x = 1.15,
    y = 0.02,
    size = 2,
    text = "<b><i>Figure 2d<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
      layout(
    title = "Actual ATAR vs. Expected ATAR Across Different Perseverance Types"
    , xaxis = x, yaxis = y) 
p1


```

##
```{r, message = FALSE}
Perseverance.measure.1 <- resc$I.believe.it.is.best.to.forgive.and.forget.
Perseverance.measure.2 <- resc$I.finish.things.despite.obstacles.in.the.way.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

orper1 = factor(Perseverance.measure.1, levels=levels(Perseverance.measure.1)[c(4,2,1,3)])
orper2 = factor(Perseverance.measure.2, levels=levels(Perseverance.measure.2)[c(4,2,1,3)])

fit <- lm(aATAR ~ eATAR, data = resc)

x <- list(
  title = "Expected ATAR"
)

y <- list(
  title = "Actual ATAR"
)

p1 <- plot_ly(resc, x = ~eATAR, y = ~aATAR, color = ~orper2, type = "scatter", mode = "markers", 
        marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1"), text = ~paste("I finish things despite obstacles in the way: ", Perseverance.measure.1, '<br>Expected ATAR:', eATAR,'<br>Actual ATAR:', aATAR)) %>%
  
  add_lines(
    x = ~eATAR,
    y = fitted(fit),
    showlegend = FALSE
  )%>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.57,
    y = 1.02,
    size = 2,
    text = "<b><i>'I finish things despite obstacles in the way'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 1.15,
    y = 0.02,
    size = 2,
    text = "<b><i>Figure 2e<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
      layout(
    title = "Actual ATAR vs. Expected ATAR Across Different Perseverance Types"
    , xaxis = x, yaxis = y) 
p1


```

##
```{r, message = FALSE}
Perseverance.measure.1 <- resc$I.believe.it.is.best.to.forgive.and.forget.
Perseverance.measure.2 <- resc$I.finish.things.despite.obstacles.in.the.way.
Perseverance.measure.3 <- resc$I.know.that.I.will.succeed.with.the.goals.I.set.for.myself.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

orper1 = factor(Perseverance.measure.1, levels=levels(Perseverance.measure.1)[c(4,2,1,3)])
orper2 = factor(Perseverance.measure.2, levels=levels(Perseverance.measure.2)[c(4,2,1,3)])
orper3 = factor(Perseverance.measure.3, levels=levels(Perseverance.measure.3)[c(4,2,1,3)])

fit <- lm(aATAR ~ eATAR, data = resc)

x <- list(
  title = "Expected ATAR"
)

y <- list(
  title = "Actual ATAR"
)

p1 <- plot_ly(resc, x = ~eATAR, y = ~aATAR, color = ~orper3, type = "scatter", mode = "markers", 
        marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1"), text = ~paste("I know that I will succeed with the goals I set for myself: ", Perseverance.measure.1, '<br>Expected ATAR:', eATAR,'<br>Actual ATAR:', aATAR)) %>%
  
  add_lines(
    x = ~eATAR,
    y = fitted(fit),
    showlegend = FALSE
  )%>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.57,
    y = 1.02,
    size = 2,
    text = "<b><i>'I know that I will succeed with the goals I set for myself'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 1.15,
    y = 0.02,
    size = 2,
    text = "<b><i>Figure 2f<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  
      layout(
    title = "Actual ATAR vs. Expected ATAR Across Different Perseverance Types"
    , xaxis = x, yaxis = y) 
p1


```


## Investigating the Relationship between Social Intelligience and Academic Performance

- Social intelligence is a person's ability to interpret social situations
- We investigated how social intelligence might affect HSC results using a self-evaluative survey
- Background research suggested a mild correlation between social intelligence and academic achievement among high school students in India
- The inconsistencies in the medians, the lack of a discernible pattern across responses, and the small sample size contribute to difficulties in finding any relationship between the two variables

##
```{r, message = FALSE}
library(plotly)
EQ.measure.1 <- resc$I.know.how.to.handle.myself.in.different.social.situations.
EQ.measure.2 <- resc$I.enjoy.being.kind.to.others.
EQ.measure.3 <- resc$I.rarely.call.attention.to.myself.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

oreq1 = factor(EQ.measure.1, levels=levels(EQ.measure.1)[c(4,2,1,3)])
oreq2 = factor(EQ.measure.2, levels=levels(EQ.measure.2)[c(4,2,1,3)])
oreq3 = factor(EQ.measure.3, levels=levels(EQ.measure.3)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~oreq1, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'I know how to handle myself in different social situations'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.18,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 3a<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Social Intelligient Types"
    , xaxis = x, yaxis = y) 
p1

```

##
```{r, message = FALSE}
library(plotly)
EQ.measure.1 <- resc$I.know.how.to.handle.myself.in.different.social.situations.
EQ.measure.2 <- resc$I.enjoy.being.kind.to.others.
EQ.measure.3 <- resc$I.rarely.call.attention.to.myself.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

oreq1 = factor(EQ.measure.1, levels=levels(EQ.measure.1)[c(4,2,1,3)])
oreq2 = factor(EQ.measure.2, levels=levels(EQ.measure.2)[c(4,2,1,3)])
oreq3 = factor(EQ.measure.3, levels=levels(EQ.measure.3)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~oreq2, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'I enjoy being kind to others'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.18,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 3b<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Social Intelligent Types"
    , xaxis = x, yaxis = y) 
p1

```

##
```{r, message = FALSE}
library(plotly)
EQ.measure.1 <- resc$I.know.how.to.handle.myself.in.different.social.situations.
EQ.measure.2 <- resc$I.enjoy.being.kind.to.others.
EQ.measure.3 <- resc$I.rarely.call.attention.to.myself.
eATAR <- resc$What.ATAR.did.you.expect.to.achieve.in.your.final.year.of.highschool...round.up.value.
aATAR <- resc$What.ATAR.did.you.actually.achieve.in.your.final.year.of.highschool...round.up.value.

oreq1 = factor(EQ.measure.1, levels=levels(EQ.measure.1)[c(4,2,1,3)])
oreq2 = factor(EQ.measure.2, levels=levels(EQ.measure.2)[c(4,2,1,3)])
oreq3 = factor(EQ.measure.3, levels=levels(EQ.measure.3)[c(4,2,1,3)])

x <- list(
  title = "Actual ATAR"
)

y <- list(
  title = ""
)

p1 <- plot_ly(resc, x = ~aATAR, color = ~oreq3, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8, marker=list( size=6 , opacity=0.9), colors=c("dodgerblue4", "burlywood1")) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = 0.535,
    y = 1.02,
    size = 2,
    text = "<b><i>'I rarely call attention to myself'<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
  add_annotations(
    xref = "paper",
    yref = "paper",
    x = -0.18,
    y = 1.06,
    size = 2,
    text = "<b><i>Figure 3c<br>
            </b></i>",
    showarrow = FALSE
    
  ) %>%
  
    
      layout(
    title = "Actual ATAR Across Different Social Intelligent Types"
    , xaxis = x, yaxis = y) 
p1

```

## Conclusion
- Therefore, failure to discern any significant trend or relationship between personality traits and academic performance meant findings of the study could not be conclusive but only implied.
- Given if the experiments were done with larger samples and more detailed and accurate testing methods, these could represent a significant improvement for our study.